A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-12 docs/methods/significance_and_novelty.tex
worked on significance

\begin{document}
\begin{center}
  {\bf Significance and Novelty} \\
  A boundary-integral framework to simulate \\ viscous erosion of a
  porous medium \\
  Bryan D.~Quaife and M.~Nicholas J.~Moore
\end{center}
In this paper we describe a numerical method to simulate viscous erosion
of a two-dimensional porous medium with a long-term goal of simulating
groundwater erosion.  Based on previous experimental results, the
erosion rate is assumed to be proportional to the magnitude of the shear
stress.  To increase the numerical stability, this law is supplemented
with a regularization term that penalizes high curvature regions.  We
avert stiffness with a change of variables that results in a system of
differential equations with a stiff linear, and these are solved with a
second-order exponential time stepping method.

To compute the shear stress, we assume the fluid is viscous---a
standard model for groundwater flow.  Then, the governing equations
(incompressible Stokes) are formulated as a well-conditioned boundary
integral equation formulation.  The integral equation resolves
inter-body interactions and is discretized with spectral accuracy and
solved with fast-multipole-accelerated GMRES.  Then, to further
characterize the flow, we compute the drag of the bodies and the
vorticity in the bulk which is used to characterize the erosion rate.

>>>>

\begin{document}
\begin{center}
  {\bf Significance and Novelty} \\
  A boundary-integral framework to simulate \\ viscous erosion of a
  porous medium \\
  Bryan D.~Quaife and M.~Nicholas J.~Moore
\end{center}
In this paper we describe a numerical method to simulate viscous erosion
of a two-dimensional porous medium.  This is a step towards a long-term
goal of developing stable, accurate, and fast numerical methods to
simulate and understand groundwater erosion.

Based on previous experimental results, the erosion rate is assumed to
be proportional to the magnitude of the shear stress.  To increase the
numerical stability, this law is supplemented with a regularization term
that penalizes high curvature regions and smooths the erosion rate at
regions where the shear stress changes sign.  We use a change of
variables to linearize stiffness, and the resulting system of
differential equations is solved with a second-order exponential time
stepping method.

To compute the shear stress, we assume the fluid is viscous---a standard
model for groundwater flow.  The governing equations (incompressible
Stokes) are formulated as a well-conditioned boundary integral equation.
The integral equation discretion resolves the non-negligible inter-body
interactions with spectral accuracy and is solved with
fast-multipole-accelerated GMRES.  To further characterize the flow, we
compute the drag of the bodies and the vorticity in the bulk which is
used to characterize the erosion rate.
